The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2023-01-24 src/tex/ms.tex
added talks to ignore
addressed minor comments from review

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}, while theoretical predictions vary greatly due to uncertainties in the aforementioned metallicity of star formation \citep[e.g.,][]{Santoliquido+2021,Broekgaarden+2021b}. In order to correctly model and interpret these observations, it is thus fundamental to know the rate of star formation at different metallicities throughout cosmic history; i.e. the metallicity-dependent cosmic star formation history \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}. Throughout this work little $z$ refers to the redshift and $Z$ to the metallicity of star formation.

@@

The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the GSMF galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}. However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}. Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.

@@

%% SFR(z) %%
\subsection{The cosmic metallicity density distribution}
For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

The skewed-log-normal distribution of metallicities is defined as:
\begin{equation}
\begin{aligned}
\label{eq: pure log skew}
\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
&= \frac{1}{Z} \times \frac{2}{\omega}
    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
                 }_{(a)}
    \underbrace {
                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
                }_{(b)},
\end{aligned}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations. The top panel shows the full two dimensional \SFRDzZ linear in time. Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. 
The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom panel). We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines. The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star-formation rate density.
Below we briefly discuss the IllustrisTNG simulations, and elaborate on our fitting procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IllustrisTNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.

\begin{deluxetable*}{cll | cl}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} & \colhead{SFRD(z)} & \colhead{best fit} } 
\startdata
$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05 \, \Msun\yr^{-1}\Mpc^{-3}$\\
$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.001$ &  $b$ &  $1.48 \pm 0.01$\\
$\alpha$   & shape (skewness)             & $-1.767 \pm 0.05 $ &  $c$ &  $4.45 \pm 0.01$\\
$\omega_0$ & scale at $z=0$               & $1.125  \pm 0.005$ &  $d$ &  $5.90 \pm 0.02$\\
$\omega_z$ & $z$-dependence of the scale  & $0.048  \pm 0.0001$ &   \\
\enddata
\end{deluxetable*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Determining reasonable variations of \SFRDzZ \label{ss: reasonable var}}
We consider variations in both the shape of the cosmic metallicity density distribution \dpdZ, and the shape of the overall star-formation rate density, \SFRDz. To determine the range that is reasonably allowed by observations, we compare our variations to the observation-based \SFRDzZ models described in \cite{Chruslinska+2021}.

For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}), while keeping all other parameters fixed at their fiducial value.
For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
We compare this to the models from \cite{Chruslinska+2021}\footnote{These models are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
We use the models \texttt{214f14SBBiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302f14SBBoco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021} as a representation of a very low and high metallicity star formation realisation respectively. These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation.
For every variation of our model, we inspect both the full \SFRDzZ and slices at redshifts $z = 0, 0.5, 3.0$ and $6$ by eye. At each slice we compare our model variation to the aforementioned low and high metallicity models, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ. This also serves as a sanity check for the overall star-formation rate density.

Lastly, we consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}). 
We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density. We choose \cite{Madau+2017} as an approximation of the lower limit. For the upper limit, we use the upper edge for the \texttt{SB: B18/C17} model variations with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig. 11]{Chruslinska+2021}. To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description for the  \texttt{SB: B18/C17} model variations as presented in appendix B1 from \cite{Chruslinska+2021}.
We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\

@@

% The location of features is robust
The first thing we note is that the location of the features in the primary mass distribution are robust against variations in \SFRDzZ.
For the stable channel, two features are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a bump at $\Mbheen\approx22\Msun$. 
Two more features are visible in at the high mass end for almost all \SFRDzZ; a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$. Although the locations of these features are constant, the features themself can disappear for variations that suppress the rate of high mass BHs (e.g., dashed lines in the top panels of Fig. \ref{fig: stable mass dists}).  
Similarly, the CE channel displays a kink in the distribution at about $9\Msun$, and a peak at approximately $\Mbheen\approx17\Msun$ for all variations. The latter peak is the global peak of the mass distribution in almost all variations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
% Grant Acknowledgements
The authors acknowledge partial financial support from the  National Science Foundation under Grant No. (NSF grant number 2009131  and PHY-1748958).”
, the Netherlands Organisation for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728 and the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063). 
\end{acknowledgments}

@@

\begin{figure}
\centering
\script{LowHighZ_fraction.py}
\includegraphics[width=0.75\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
\caption{Percentage of stellar mass formed at low metallicity ($Z < 0.1 \rm{Z_{\odot}}$) , versus high metallicity ($Z>\rm{Z_{\odot}}$) for all star formation below a certain threshold redshift: $z<0.5$ (left), $z < 3.0$ (middle) and $z<10$ (right). Data from observation-based variations are shown with semi-transparent thick crosses,  \citep[][]{Chruslinska2019_obs} and semi-transparent thick plus signs \citep[][]{Chruslinska+2021}, the low- and high-metallicity extremes are indicated with opague symbols. For data from cosmological simulations, we follow \cite{Pakmor+2022} and show Illustris \citep[][squares]{Vogelsberger+2014}, Simba \citep[][diamonds]{Dave+2019}, EAGLE \citep[][triangles]{Schaye+2015}, TNG50 and TNG100 \citep[][filled and open circles respectively]{FirstResTNG_Springel2018}. Black thin crosses display variations of the cosmic metallicity density distribution that is part of our fiducial \SFRDzZ. The parameter that is varied with respect to the fiducial and its new value are annotated. This shows that our \SFRDzZ variations span the range of reasonable cosmic metallicity density distributions as determined by observation-based and cosmological simulations-based models.
\label{fig: low high Z fraction}
  }
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Make sure to address the difference in rate between this paper and \citep{vanson2022_lowMbh}!}
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}, while theoretical predictions vary greatly due to uncertainties in the aforementioned metallicity of star formation \citep[e.g.,][]{Santoliquido+2021,Broekgaarden+2021b}. In order to correctly model and interpret these observations, it is thus fundamental to know the rate of star formation at different metallicities throughout cosmic history; i.e. the metallicity-dependent cosmic star formation history \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}. Throughout this work little $z$ refers to the redshift and $Z$ to the metallicity of star formation.

@@

The first method is based on empirical scaling relations, linking galaxy properties like stellar mass $M_{\star}$, metallicity $Z$, and overall star-formation rate density \SFRDz, with the galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}. However, the applied methods to infer galaxy properties and subsequently scaling relations such as the MZ-relation differ greatly, which makes it difficult to interpret these results in a consistent way \citep[e.g.,][]{KewleyEllison2008,MaiolinoMannucci2019,Cresci+2019}. Moreover, observations are generally incomplete at high redshifts and low galaxy luminosity \citep[e.g.,][]{Chruslinska+2021}.

@@

%% SFR(z) %%
\subsection{The cosmic metallicity density distribution}
For the probability distribution of metallicities we draw inspiration from the approach by e.g., \cite{Neijssel+2019} who used a log-normal distribution for their phenomenological model. \edit1{Unfortunately, a simple log-normal distribution cannot capture the asymmetry that we see in the cosmological simulations}, which show an extended tail in  $\log_{10} Z$ towards low metallicity, combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

The skewed-log-normal distribution of metallicities is defined as:
\begin{equation}
\begin{aligned}
\label{eq: pure log skew}
\mathrm{\frac{dP}{dZ}}(Z, z) &= \frac{1}{Z} \times \frac{\mathrm{dP(}Z,z) }{{\rm d}\ln Z}  \\
&= \frac{1}{Z} \times \frac{2}{\omega}
    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
                 }_{(a)}
    \underbrace {
                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
                }_{(b)},
\end{aligned}
\end{equation}

@@

We fit our new functional form of \SFRDzZ as defined by equations \ref{eq: total sfrd}, \ref{eq: z log skew} and \ref{eq: sfr1} to the IllustrisTNG cosmological simulations. 
We simultaneously fit for the following nine free parameters $\alpha, \mu_0, \mu_z, \omega_0, \omega_z$, which govern the metallicity dependence and $a,b, c$ and $d$, which set the overall star-formation rate density.
Below we briefly discuss the IllustrisTNG simulations, and elaborate on our fitting procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IllustrisTNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity-dependent cosmic star formation history\footnote{\edit1{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Notebooks/Fit_model_to_sfrdzZ.ipynb} } }.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resulting \SFRDzZ}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{FitComparison_3panelPlot.py}
\includegraphics[width=0.9\textwidth]{figures/SFRD_FIT_evaluation_compare.pdf}
\caption{Our fiducial \SFRDzZ model, adopting the best fitting parameters (listed on the top right) to fit the TNG100 simulations. The top panel shows the full two dimensional \SFRDzZ linear in time. Contours range from $10^{-7} - 10^{-2} \Msun \yr^{-1}\Mpc^{-3}$. 
The bottom left (right) panel shows slices of the distribution in redshift (metallicity). Each slice is displaced by 0.01$\Msun \yr^{-1}\Mpc^{-3}$ (note the linear scale of \SFRDzZ in the bottom panel). We show the TNG100 simulation data with thick gray lines. 
For comparison, we also show the phenomenological model from \protect\cite{Neijssel+2019} in all panels with grey dotted lines. The bottom panels show that our analytical model adequately captures the shape of the \SFRDzZ from TNG100.
 \label{fig: fit SFRD}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our best fitting parameters are listed in Table \ref{tab: fit params}. With these fit parameters, $\chi^2(z_j)$ is smaller than $2\cdot 10^{-4}$ at any given redshift. We will refer to the \SFRDzZ with the parameters listed in Table \ref{tab: fit params} as our fiducial model.

\begin{deluxetable*}{cll | cl}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} &  \colhead{SFRD(z)} & \colhead{best fit} \\
 \colhead{ } & \colhead{} & \colhead{}  & \colhead{$\Msun\yr^{-1}\Mpc^{-3}$} & \colhead{} } 
\startdata
$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.001$ &  $b$ &  $1.48 \pm 0.01$\\
$\alpha$   & shape (skewness)             & $-1.767 \pm 0.05 $ &  $c$ &  $4.45 \pm 0.01$\\
$\omega_0$ & scale at $z=0$               & $1.125  \pm 0.005$ &  $d$ &  $5.90 \pm 0.02$\\
$\omega_z$ & $z$-dependence of the scale  & $0.048  \pm 0.0001$ &   \\
\enddata
\end{deluxetable*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Determining reasonable variations of \SFRDzZ \label{ss: reasonable var}}
We consider variations in both the shape of the cosmic metallicity density distribution \dpdZ, and the shape of the overall star-formation rate density, \SFRDz. To determine the range that is reasonably allowed by observations, we compare our variations to the observation-based \SFRDzZ models described in \cite{Chruslinska+2021}.
\edit1{An overview of the explored variations is shown in Table \ref{tab: fit variations}. Below we explain how we arrive at these values.  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable}{cccc}
\label{tab: fit variations}
\tablewidth{0.5\textwidth} 
\tablecaption{\edit1{Variations on \SFRDzZ. 
For every variation, we either swap the value of an individual \dpdZ parameter, or exchange the set of four \SFRDz parameters, and replace them by the the min/max values listed here. All other parameters are kept fixed at their fiducial value. }}
\tablehead{\colhead{} & \colhead{min} & \colhead{fiducial} & \colhead{max} } 
\startdata
\dpdZ &       &  &  \\
$\mu_0$          &   0.007   & $0.025$  &  0.035  \\
$\mu_z$          &   0.0   & $-0.048$ &   -0.5 \\
$\alpha$         &   -6.0   & $-1.767$ &  0.0  \\
$\omega_0$       &   0.7   & $1.125$  &  2.0  \\
$\omega_z$       &   0.0   & $0.048$  &  0.1  \\ \hline
\SFRDz &       &  &  \\
($a$,$b$ ... &  ($0.01$, $2.60$   & ($0.02$, $1.48$ &  ($0.03$, $2.6$ \\
... $c$,$d$) &  $3.20$, $6.20$)   & $4.45$, $5.90$) &   $3.3$, $5.9$) \\
% \parbox{1.75cm}{($a$,$b$, \hspace{0.7cm} $c$,$d$)} &  \parbox{1.75cm}{($0.01$, $2.60$, $3.20$, $6.20$)}   & \parbox{1.75cm}{($0.02$, $1.48$, $4.45$, $5.90$)} &  \parbox{1.75cm}{($0.03$, $2.6$, $3.3$, $5.9$)} \\
\enddata
\end{deluxetable}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}), while keeping all other parameters fixed at their fiducial value.
For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively. These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation, 
%
\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon. The difference between these models lies in the assumptions in the underlying empirical galaxy relations. In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities. }
% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
%
\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies), 
and a galaxy mass-metallicity relation following \cite{PettiniPagel2004}. 
This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}. Including starbursts shift the peak of \SFRDzZ to lower metallicities and broadens the low metallicity part of the distribution.
}
% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
%
\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function that is constant over redshift, and a galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}. Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies. 
}

%

For every variation of our model, we inspect both the full \SFRDzZ and slices at redshifts $z = 0, 0.5, 3.0$ and $6$ by eye. At each slice we compare our model variation to \edit1{\texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ}}, and ensure that none of our variations significantly exceeds these extremes in \SFRDzZ. This also serves as a sanity check for the overall star-formation rate density.

Lastly, we consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}). 
We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density. We choose \cite{Madau+2017} as an approximation of the lower limit. 
For the upper limit, we use the upper edge of 
\edit1{ models that adopt starbursts following \cite{Bisigello+2018} and \cite{Caputi+2017} (\texttt{SB: B18/C17}), combined}
with a non-evolving low-mass end of the galaxy stellar mass function \citep[shown as a thick brown line in Fig. 11 of ][and described in their table B1]{Chruslinska+2021}.
% for the \texttt{SB: B18/C17} model variations (i.e. ) with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig. 11]{Chruslinska+2021}. 
To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description of this model as presented in appendix B1 of \cite{Chruslinska+2021}.
We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\

@@

% The location of features is robust
The first thing we note is that the location of the features in the primary mass distribution are robust against variations in \SFRDzZ.
For the stable channel, two features are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a bump at $\Mbheen\approx22\Msun$. 
Two more features are visible in at the high mass end for almost all \SFRDzZ; a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$. Although the locations of these features are constant, the features themselves can disappear for variations that suppress the rate of high mass BHs (e.g., dashed lines in the top panels of Fig. \ref{fig: stable mass dists}).  
Similarly, the CE channel displays a kink in the distribution at about $9\Msun$, and a peak at approximately $\Mbheen\approx17\Msun$ for all variations. The latter peak is the global peak of the mass distribution in almost all variations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
% Grant Acknowledgements
The authors acknowledge partial financial support from the  National Science Foundation under Grant No. (NSF grant number 2009131  and PHY-1748958).”
, the Netherlands Organisation for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728 and the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063). 
This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958. %KITP acknowledgement
%as follows: This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.
\end{acknowledgments}

@@

\begin{figure}
\centering
\script{LowHighZ_fraction.py}
\includegraphics[width=0.75\textwidth]{figures/High_Low_metalFractionSFMass.pdf}
\caption{Percentage of stellar mass formed at low metallicity ($Z < 0.1 \rm{Z_{\odot}}$) , versus high metallicity ($Z>\rm{Z_{\odot}}$) for all star formation below a certain threshold redshift: $z<0.5$ (top), $z < 3.0$ (middle) and $z<10$ (bottom). Data from observation-based variations are shown with semi-transparent thick crosses,  \citep[][]{Chruslinska2019_obs} and semi-transparent thick plus signs \citep[][]{Chruslinska+2021}, the low- and high-metallicity extremes are indicated with opaque symbols. For data from cosmological simulations, we follow \cite{Pakmor+2022} and show Illustris \citep[][squares]{Vogelsberger+2014}, Simba \citep[][diamonds]{Dave+2019}, EAGLE \citep[][triangles]{Schaye+2015}, TNG50 and TNG100 \citep[][filled and open circles respectively]{FirstResTNG_Springel2018}. Black thin crosses display variations of the cosmic metallicity density distribution that is part of our fiducial \SFRDzZ. The parameter that is varied with respect to the fiducial and its new value are annotated. This shows that our \SFRDzZ variations span the range of reasonable cosmic metallicity density distributions as determined by observation-based and cosmological simulations-based models.
\label{fig: low high Z fraction}
  }
\end{figure}
